---
title: "Section 1 - Market-Level Analysis"
author: "Rocky Rowell"
date: "2026-06-09"
output: pdf_document
header-includes:
  - \usepackage[normalem]{ulem}
---

***
# Description
This file is one of the analysis files in the project. All market-level analysis 
is conducted in this file. The first form of analysis is a set of exploratory 
graphs observing each outcome variable over the sample period, grouped by game-age. 
The second form of analysis is a set of graphs comparing outcome variables for 
Steam-only, Dual-Platform, and Future Dual-Platform games after Epic's launch, 
also grouped by game-age. The final form of analysis is a set of regression models
that examine the change in outcome variable trajectories for Steam-only and 
Dual-Platform games relative to 2018. These regression models are visualized 
through a set of graphs.

# Notes / Important Information
- Although the No-Game-FE models are created in this file, they are not used in 
the thesis.
- 2013 dropped from graphs and regressions (low sample size = high volatility). 
2013 only includes a few weeks of data in this sample, which messes with the graphs. 
- Regression models account for time trends and seasonality with 
log(Quarters Since Release) and month-of-year fixed effects

***
# Setup and Data Cleaning
```{r echo=TRUE, message=FALSE, warning=FALSE}
# Libraries
library(tidyverse)
library(fixest)
library(ggthemes)
library(patchwork)
library(modelsummary)
library(flextable)

# Data
data <- read_csv("Data/cleaned_data.csv")
```

## Shared Globals
```{r echo=TRUE, message=FALSE, warning=FALSE}
epic_launch <- as.Date("2018-12-01")

# updated game age windows: 0-6mo, 6mo-2yr, 2yr+
graph_windows <- list(
  "0-6 Months" = c(0,   182),
  "6 Months - 2 Years"  = c(182, 730),
  "2+ Years"   = c(730, Inf)
)

genre_cols <- c("RPG","Action","Adventure","Shooter","Strategy","Simulation",
                "Platformer","Puzzle","Horror","OpenWorld","Survival",
                "Roguelike","Multiplayer","Narrative")
```

## Epic Entry Dates
```{r echo=TRUE, message=FALSE, warning=FALSE}
epic_entry_dates <- data %>%
  filter(shop_name == "Epic") %>%
  group_by(game_title) %>%
  summarise(entry_date = min(date), .groups = "drop")
```

***
# Section 1.1: Full Sample Exploratory Graphs

Monthly average Steam prices, sale frequency, and discount depth. Three
game-age windows (0-6 months, 6 months to 2 years, 2+ years). Includes
95% CI ribbons around the trend lines.

## Helper: build monthly panel for a given age range
```{r echo=TRUE, message=FALSE, warning=FALSE}
build_window_panel <- function(age_range, min_frac = 0.05) {
  panel <- data %>%
    filter(shop_name == "Steam") %>%
    mutate(days_since_release = as.numeric(date - release_date)) %>%
    filter(days_since_release >= age_range[1],
           days_since_release <  age_range[2]) %>%
    mutate(month = floor_date(date, "month")) %>%
    filter(month < as.Date("2024-12-01")) %>%
    group_by(month) %>%
    summarise(
      avg_real_price = mean(real_price,       na.rm = TRUE),
      avg_sale_freq  = mean(sale,             na.rm = TRUE),
      avg_disc_depth = mean(discount_percent, na.rm = TRUE),
      n_games        = n_distinct(game_title),
      .groups        = "drop"
    ) %>%
    filter(year(month) > 2013)

  thresh <- median(panel$n_games) * min_frac
  panel %>%
    filter(n_games >= thresh) %>%
    mutate(period = if_else(month < epic_launch, "Pre-Epic", "Post-Epic"))
}
```

## Helper: pre/post period averages for annotation
```{r echo=TRUE, message=FALSE, warning=FALSE}
compute_period_avgs <- function(df) {
  df %>%
    group_by(period) %>%
    summarise(
      avg_real_price = mean(avg_real_price, na.rm = TRUE),
      avg_sale_freq  = mean(avg_sale_freq,  na.rm = TRUE),
      avg_disc_depth = mean(avg_disc_depth, na.rm = TRUE),
      label_x        = mean(month),
      .groups        = "drop"
    )
}
```

## Helper: single-outcome plot for one window (with 95% CI)
```{r echo=TRUE, message=FALSE, warning=FALSE}
plot_window_outcome <- function(df, period_avgs, outcome_col, y_lab,
                                window_label, label_format = "raw") {
  label_df <- period_avgs %>%
    mutate(
      lbl = case_when(
        label_format == "dollar"  ~ paste0("Avg: $", round(.data[[outcome_col]], 2)),
        label_format == "percent" ~ paste0("Avg: ",  round(.data[[outcome_col]], 2), "%"),
        TRUE                      ~ paste0("Avg: ",  round(.data[[outcome_col]], 2))
      )
    )

  ggplot(df, aes(x = month, y = .data[[outcome_col]])) +
    geom_line(color = "steelblue", linewidth = 0.6) +
    geom_smooth(aes(group = period), method = "lm", se = TRUE,
                color = "firebrick", fill = "firebrick",
                alpha = 0.15, linewidth = 0.9) +
    geom_vline(xintercept = epic_launch,
               linetype = "dashed", color = "black") +
    geom_label(data = label_df,
               aes(x = label_x, y = .data[[outcome_col]], label = lbl),
               color = "firebrick", size = 3, fill = "white") +
    labs(
      subtitle = window_label,
      x = NULL, y = y_lab
    ) +
    theme_fivethirtyeight() +
    theme(
      plot.subtitle = element_text(face = "bold", hjust = 0.5),
      plot.background  = element_rect(fill = "white", color = NA),
      panel.background = element_rect(fill = "#F7F7F7", color = NA)
      )
}
```

## Build all three window datasets and period averages
```{r echo=TRUE, message=FALSE, warning=FALSE}
window_data <- map(graph_windows, build_window_panel)
window_avgs <- map(window_data, compute_period_avgs)
```

## Real Price Plots
```{r fig.width=12, fig.height=4, echo=TRUE, message=FALSE, warning=FALSE}
p_price <- map2(names(window_data), window_data, function(nm, df) {
  plot_window_outcome(df, window_avgs[[nm]], "avg_real_price",
                      "Avg Real Price (USD)", nm, label_format = "dollar")
})

(p_price[[1]] | p_price[[2]] | p_price[[3]]) +
  plot_annotation(
    title    = "Monthly Average Real Price on Steam",
    subtitle = "By game age window | dashed = Epic launch"
  ) &
  coord_cartesian(ylim = c(10, 35))
```

## Sale Frequency Plots
```{r fig.width=12, fig.height=4, echo=TRUE, message=FALSE, warning=FALSE}
p_sale <- map2(names(window_data), window_data, function(nm, df) {
  plot_window_outcome(df, window_avgs[[nm]], "avg_sale_freq",
                      "Avg Sale Frequency", nm, label_format = "raw")
})

(p_sale[[1]] | p_sale[[2]] | p_sale[[3]]) +
  plot_annotation(
    title    = "Monthly Average Sale Frequency on Steam",
    subtitle = "By game age window | dashed = Epic launch"
  ) &
  coord_cartesian(ylim = c(0, .55))
```

## Discount Depth Plots
```{r fig.width=12, fig.height=4, echo=TRUE, message=FALSE, warning=FALSE}
p_disc <- map2(names(window_data), window_data, function(nm, df) {
  plot_window_outcome(df, window_avgs[[nm]], "avg_disc_depth",
                      "Avg Discount Depth (%)", nm, label_format = "percent")
})

(p_disc[[1]] | p_disc[[2]] | p_disc[[3]]) +
  plot_annotation(
    title    = "Monthly Average Discount Depth on Steam",
    subtitle = "By game age window | dashed = Epic launch"
  ) &
  coord_cartesian(ylim = c(0, 32))
```


***
# Section 1.2: Steam-Only vs Dual-Platform vs Future Dual-Platform

Restricts to the post-Epic-launch period and splits the Steam catalog into
three groups:
- Steam-Only: never joins Epic
- Dual-Platform: currently listed on Epic (date >= entry_date)
- Future Dual-Platform: will join Epic but has not yet (date < entry_date,
  entry_date not NA)

Same age windows as above. Includes 95% CI ribbons.

## Helper: build post-launch panel with three groups
```{r echo=TRUE, message=FALSE, warning=FALSE}
build_postlaunch_panel <- function(age_range, min_frac = 0.05) {
  panel <- data %>%
    filter(shop_name == "Steam") %>%
    mutate(days_since_release = as.numeric(date - release_date)) %>%
    filter(days_since_release >= age_range[1],
           days_since_release <  age_range[2]) %>%
    filter(date >= epic_launch) %>%
    left_join(epic_entry_dates, by = "game_title") %>%
    mutate(
      group = case_when(
        is.na(entry_date)          ~ "Steam-Only",
        date >= entry_date         ~ "Dual-Platform",
        date <  entry_date         ~ "Future Dual-Platform",
        TRUE                       ~ NA_character_
      ),
      month = floor_date(date, "month")
    ) %>%
    filter(month < as.Date("2024-12-01")) %>%
    group_by(group, month) %>%
    summarise(
      avg_real_price = mean(real_price,       na.rm = TRUE),
      avg_sale_freq  = mean(sale,             na.rm = TRUE),
      avg_disc_depth = mean(discount_percent, na.rm = TRUE),
      n_games        = n_distinct(game_title),
      .groups        = "drop"
    )

  # Drop sparse months WITHIN each group (per-group median, so each
  # series is trimmed on its own scale rather than a pooled one)
  panel %>%
    group_by(group) %>%
    filter(n_games >= median(n_games) * min_frac) %>%
    ungroup()
}
```

## Helper: % of Dual/Future-DP games actually on Epic within window
```{r echo=TRUE, message=FALSE, warning=FALSE}
pct_on_epic_in_window <- function(age_range) {
  data %>%
    filter(shop_name == "Steam") %>%
    distinct(game_title, release_date) %>%
    left_join(epic_entry_dates, by = "game_title") %>%
    filter(!is.na(entry_date)) %>%
    mutate(
      days_to_epic      = as.numeric(entry_date - release_date),
      on_epic_in_window = days_to_epic >= age_range[1] &
                           days_to_epic <  age_range[2]
    ) %>%
    summarise(pct = mean(on_epic_in_window, na.rm = TRUE) * 100) %>%
    pull(pct) %>%
    round(1)
}
```

## Helper: three-group plot with 95% CI ribbons
```{r echo=TRUE, message=FALSE, warning=FALSE}
plot_group_comparison <- function(df, outcome_col, y_lab,
                                  window_label, pct_on_epic) {
  ggplot(df, aes(x = month, y = .data[[outcome_col]], color = group, fill = group)) +
    geom_line(linewidth = 0.5, alpha = 0.5) +
    geom_smooth(method = "lm", se = TRUE, linewidth = 0.9, alpha = 0.15) +
    scale_color_manual(
      values = c("Steam-Only"           = "steelblue",
                 "Dual-Platform"        = "firebrick",
                 "Future Dual-Platform" = "darkorange"),
      name   = NULL
    ) +
    scale_fill_manual(
      values = c("Steam-Only"           = "steelblue",
                 "Dual-Platform"        = "firebrick",
                 "Future Dual-Platform" = "darkorange"),
      name   = NULL
    ) +
    labs(
      subtitle = paste0(window_label),
      x = NULL, y = y_lab
    ) +
    theme_fivethirtyeight() +
    theme(
      plot.subtitle = element_text(face = "bold", hjust = 0.5),
      plot.background  = element_rect(fill = "white", color = NA),
      panel.background = element_rect(fill = "#F7F7F7", color = NA),
      legend.position  = "bottom",
      legend.background = element_rect(fill = NA, color = NA),
      legend.key        = element_rect(fill = NA, color = NA)
      )
}
```

## Build post-launch datasets
```{r echo=TRUE, message=FALSE, warning=FALSE}
postlaunch_data <- map(graph_windows, build_postlaunch_panel)
postlaunch_pct  <- map(graph_windows, pct_on_epic_in_window)
```

## Real Price Comparison
```{r fig.width=13, fig.height=4.5, echo=TRUE, message=FALSE, warning=FALSE}
pl_price <- map2(names(postlaunch_data), postlaunch_data, function(nm, df) {
  plot_group_comparison(df, "avg_real_price", "Avg Real Price (USD)",
                        nm, postlaunch_pct[[nm]])
})

(pl_price[[1]] | pl_price[[2]] | pl_price[[3]]) +
  plot_annotation(
    title    = "Post-Launch Real Price on Steam",
    subtitle = "By Game Age Window | Trend lines with 95% CI"
  ) +
  plot_layout(guides = "collect") &
  theme(legend.position = "bottom") &
  coord_cartesian(ylim = c(10, 55))
```

## Sale Frequency Comparison
```{r fig.width=13, fig.height=4.5, echo=TRUE, message=FALSE, warning=FALSE}
pl_sale <- map2(names(postlaunch_data), postlaunch_data, function(nm, df) {
  plot_group_comparison(df, "avg_sale_freq", "Avg Sale Frequency",
                        nm, postlaunch_pct[[nm]])
})

(pl_sale[[1]] | pl_sale[[2]] | pl_sale[[3]]) +
  plot_annotation(
    title    = "Post-Launch Sale Frequency on Steam",
    subtitle = "By Game Age Window | Trend lines with 95% CI"
  ) +
  plot_layout(guides = "collect") &
  theme(legend.position = "bottom") &
  coord_cartesian(ylim = c(0, .6))
```

## Discount Depth Comparison
```{r fig.width=13, fig.height=4.5, echo=TRUE, message=FALSE, warning=FALSE}
pl_disc <- map2(names(postlaunch_data), postlaunch_data, function(nm, df) {
  plot_group_comparison(df, "avg_disc_depth", "Avg Discount Depth (%)",
                        nm, postlaunch_pct[[nm]])
})

(pl_disc[[1]] | pl_disc[[2]] | pl_disc[[3]]) +
  plot_annotation(
    title    = "Post-Launch Discount Depth on Steam",
    subtitle = "By Game Age Window | Trend lines with 95% CI"
  ) +
  plot_layout(guides = "collect") &
  theme(legend.position = "bottom") &
  coord_cartesian(ylim = c(0, 35))
```


***
# Section 1.3: Regression Models

Two model families per outcome. Model 1 has no game FE with genre controls;
Model 2 has game FE (genres absorbed).

## Build Regression Dataset
```{r echo=TRUE, message=FALSE, warning=FALSE}
reg_data <- data %>%
  filter(shop_name == "Steam") %>%
  mutate(month = floor_date(date, "month")) %>%
  group_by(game_title, month) %>%
  summarise(
    avg_real_price = mean(real_price,       na.rm = TRUE),
    avg_price      = mean(price,            na.rm = TRUE),
    avg_sale_freq  = mean(sale,             na.rm = TRUE),
    avg_disc_depth = mean(discount_percent, na.rm = TRUE),
    release_date   = first(release_date),
    across(all_of(genre_cols), first),
    .groups = "drop"
  ) %>%
  filter(year(month) > 2013) %>%
  left_join(epic_entry_dates, by = "game_title") %>%
  mutate(
    ever_on_epic           = as.integer(!is.na(entry_date)),
    year                   = year(month),
    month_of_year          = month(month),
    quarters_since_release = as.numeric(month - release_date) / (365.25 / 4),
    log_qsr                = log(pmax(quarters_since_release, 0) + 1)
  )
```

## Helper: run two models for one outcome
```{r echo=TRUE, message=FALSE, warning=FALSE}
genre_string <- paste(genre_cols, collapse = " + ")

run_two_models <- function(outcome, tsr_var) {
  # Model 1: no game FE, with genre + ever_on_epic + year main effects + interactions
  f1 <- as.formula(paste0(
    outcome,
    " ~ i(year, ref = 2018) + ever_on_epic + i(year, ever_on_epic, ref = 2018) + ",
    tsr_var, " + ", genre_string,
    " | month_of_year"
  ))
  m1 <- feols(f1, data = reg_data, cluster = ~ game_title)

  # Model 2: game FE (absorbs ever_on_epic and genres)
  f2 <- as.formula(paste0(
    outcome,
    " ~ i(year, ref = 2018) + i(year, ever_on_epic, ref = 2018) + ",
    tsr_var,
    " | game_title + month_of_year"
  ))
  m2 <- feols(f2, data = reg_data, cluster = ~ game_title)

  list(m1 = m1, m2 = m2)
}
```

## Nominal Price
```{r echo=TRUE, message=FALSE, warning=FALSE}
price_models <- run_two_models("avg_price", "log_qsr")

etable(price_models$m1, price_models$m2,
       headers = c("No Game FE (Model 1)", "Game FE (Model 2)"),
       title   = "Nominal Price — Full regression output (for review)")
```

## Real Price
```{r echo=TRUE, message=FALSE, warning=FALSE}
realprice_models <- run_two_models("avg_real_price", "log_qsr")

etable(realprice_models$m1, realprice_models$m2,
       headers = c("No Game FE (Model 1)", "Game FE (Model 2)"),
       title   = "Real Price — Full regression output (for review)")
```

## Sale Frequency
```{r echo=TRUE, message=FALSE, warning=FALSE}
sale_models <- run_two_models("avg_sale_freq", "log_qsr")

etable(sale_models$m1, sale_models$m2,
       headers = c("No Game FE (Model 1)", "Game FE (Model 2)"),
       title   = "Sale Frequency — Full regression output (for review)")
```

## Discount Depth
```{r echo=TRUE, message=FALSE, warning=FALSE}
disc_models <- run_two_models("avg_disc_depth", "log_qsr")

etable(disc_models$m1, disc_models$m2,
       headers = c("No Game FE (Model 1)", "Game FE (Model 2)"),
       title   = "Discount Depth — Full regression output (for review)")
```

***
# Section 1.4: Thesis Display Output
I needed to make Word output of the models for the thesis.

```{r echo=TRUE, message=FALSE, warning=FALSE}
omit_regex <- paste0("Intercept|^",
                     paste(genre_cols, collapse = "$|^"),
                     "$")

coef_rename <- c(
  "ever_on_epic"           = "Ever on Epic",
  "log_qsr"                = "Log(Quarters Since Release)",
  "quarters_since_release" = "Quarters Since Release"
)
```

```{r}
# Game FE models only (m2), one column per outcome
s1_models <- list(
  "Nominal Price (USD)" = price_models$m2,
  "Real Price (USD)"    = realprice_models$m2,
  "Sale Freq. (share)"    = sale_models$m2,
  "Discount Depth (pp)"  = disc_models$m2
)

# Build coef_map programmatically so year effects group first, then the
# interactions, then the trend. Years derived from the data (length-safe),
# 2018 dropped as the reference.
years      <- sort(setdiff(unique(reg_data$year), 2018))
year_terms <- paste0("year::", years)                  # main effects
int_terms  <- paste0("year::", years, ":ever_on_epic") # interactions

coef_map <- c(
  setNames(as.character(years), year_terms),
  setNames(paste0(years, " x Epic"), int_terms),
  "log_qsr" = "Log(QSR)"
)

s1_ft <- modelsummary(
  s1_models,
  coef_map = coef_map,
  gof_omit = "^R2$|R2 Adj\\.|R2 Within Adj\\.|AIC|BIC|Log\\.Lik\\.|RMSE|Std\\.Errors|FE:",
  stars    = c('*' = .05, '**' = .01, '***' = .001),
  title    = "Year-Relative Effects on Steam Outcomes",
  notes    = c(
    "All models include game and month-of-year fixed effects. Reference year 2018. SEs clustered by game"
  ),
  output   = "flextable"
) %>%
  flextable::autofit()

s1_ft
# save table
save_as_docx(s1_ft, path = "Output/tab_section1_regs.docx")
```

***
# Section 1.5: Year-Relative Trajectory Plots

Extracts the year main effects and their interactions from the regression
models to plot Steam-Only vs Dual-Platform trajectories relative to 2018.

## Helper: extract trajectories with 95% CI
```{r echo=TRUE, message=FALSE, warning=FALSE}
extract_trajectories <- function(model, model_label, outcome_label) {
  V  <- vcov(model)
  co <- coef(model)

  year_terms <- grep("^year::[0-9]+$", names(co), value = TRUE)
  years      <- as.numeric(sub("year::", "", year_terms))

  map_dfr(seq_along(year_terms), function(i) {
    y_term   <- year_terms[i]
    int_term <- paste0(y_term, ":ever_on_epic")

    so_est <- co[y_term]
    so_se  <- sqrt(V[y_term, y_term])

    if (int_term %in% names(co)) {
      dp_est <- co[y_term] + co[int_term]
      dp_var <- V[y_term, y_term] + V[int_term, int_term] +
                2 * V[y_term, int_term]
      dp_se  <- sqrt(dp_var)
    } else {
      dp_est <- NA_real_
      dp_se  <- NA_real_
    }

    tibble(
      model      = model_label,
      outcome    = outcome_label,
      year       = years[i],
      steam_only = so_est,
      so_se      = so_se,
      dual_plat  = dp_est,
      dp_se      = dp_se
    )
  })
}
```

## Build long-form plot dataset
```{r echo=TRUE, message=FALSE, warning=FALSE}
plot_data <- bind_rows(
  # extract_trajectories(price_models$m1,     "No Game FE", "Nominal Price"),
  extract_trajectories(price_models$m2,     "Game FE",    "Nominal Price"),
  # extract_trajectories(realprice_models$m1, "No Game FE", "Real Price"),
  extract_trajectories(realprice_models$m2, "Game FE",    "Real Price"),
  # extract_trajectories(sale_models$m1,      "No Game FE", "Sale Frequency"),
  extract_trajectories(sale_models$m2,      "Game FE",    "Sale Frequency"),
  # extract_trajectories(disc_models$m1,      "No Game FE", "Discount Depth"),
  extract_trajectories(disc_models$m2,      "Game FE",    "Discount Depth")
)

# Add reference-year (2018) rows at zero for visual continuity
ref_year_rows <- plot_data %>%
  distinct(model, outcome) %>%
  mutate(year = 2018, steam_only = 0, so_se = 0,
         dual_plat = 0, dp_se = 0)

plot_data <- bind_rows(plot_data, ref_year_rows) %>%
  arrange(model, outcome, year)

# Reshape to long form for plotting
plot_long <- plot_data %>%
  pivot_longer(cols = c(steam_only, dual_plat),
               names_to = "group", values_to = "estimate") %>%
  mutate(
    se    = if_else(group == "steam_only", so_se, dp_se),
    group = recode(group,
                   steam_only = "Steam-Only",
                   dual_plat  = "Dual-Platform"),
    ci_lower = estimate - 1.96 * se,
    ci_upper = estimate + 1.96 * se
  ) %>%
  select(model, outcome, year, group, estimate, ci_lower, ci_upper)
```

## Plot helper (faceted by model, one outcome per plot)
```{r echo=TRUE, message=FALSE, warning=FALSE}
plot_trajectories <- function(df, outcome_label) {
  df %>%
    filter(outcome == outcome_label) %>%
    ggplot(aes(x = year, y = estimate, color = group, fill = group)) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray40") +
    geom_vline(xintercept = 2018.9,
               linetype = "dotted", color = "black", alpha = 1) +
    geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper),
                alpha = 0.15, color = NA) +
    geom_line(linewidth = 0.8) +
    geom_point(size = 2) +
    # facet_wrap(~ model, nrow = 1) +
    scale_color_manual(values = c("Steam-Only"    = "steelblue",
                                   "Dual-Platform" = "firebrick"),
                       name = NULL) +
    scale_fill_manual(values  = c("Steam-Only"    = "steelblue",
                                   "Dual-Platform" = "firebrick"),
                      name = NULL) +
    scale_x_continuous(breaks = unique(df$year)) +
    labs(
      title    = paste0("Year-Relative Change in ", outcome_label),
      subtitle = "Ref = 2018 | Point estimate with 95% CI | dotted line = Epic launch",
      x        = "Year",
      y        = paste0("Change from 2018 (", outcome_label, ")")
    ) +
    theme_fivethirtyeight() +
    theme(legend.position = "bottom",
          axis.text.x     = element_text(angle = 45, hjust = 1))
}
```

## Generate one plot per outcome
```{r fig.width=12, fig.height=4.5, echo=TRUE, message=FALSE, warning=FALSE}
plot_trajectories(plot_long, "Nominal Price")
```

```{r fig.width=12, fig.height=4.5, echo=TRUE, message=FALSE, warning=FALSE}
plot_trajectories(plot_long, "Real Price")
```

```{r fig.width=12, fig.height=4.5, echo=TRUE, message=FALSE, warning=FALSE}
plot_trajectories(plot_long, "Sale Frequency")
```

```{r fig.width=12, fig.height=4.5, echo=TRUE, message=FALSE, warning=FALSE}
plot_trajectories(plot_long, "Discount Depth")
```


***
# Extra Information and Code
## Sanity checks on regression data
```{r echo=TRUE, message=FALSE, warning=FALSE}
cat("Observations by year:\n")
reg_data %>% count(year) %>% print()

cat("\nEver on Epic counts:\n")
reg_data %>%
  distinct(game_title, ever_on_epic) %>%
  count(ever_on_epic) %>% print()

cat("\nMonth-of-year distribution:\n")
reg_data %>% count(month_of_year) %>% print()
```

## Full Regression Output (No Game FE vs Game FE)
### Nominal Price — Thesis Table
```{r echo=TRUE, message=FALSE, warning=FALSE}
modelsummary(
  list("No Game FE" = price_models$m1, "Game FE" = price_models$m2),
  stars       = TRUE,
  coef_omit   = omit_regex,
  coef_rename = coef_rename,
  gof_omit    = "AIC|BIC|Log.Lik|F|RMSE",
  title       = "Nominal Price: Year-Relative Effects",
  notes       = "Reference year 2018. Year main effects show market-wide change relative to 2018; year x ever_on_epic interactions show additional differential effect on dual-platform games.",
  output = "flextable"
)
```

### Real Price — Thesis Table
```{r echo=TRUE, message=FALSE, warning=FALSE}
modelsummary(
  list("No Game FE" = realprice_models$m1, "Game FE" = realprice_models$m2),
  stars       = TRUE,
  coef_omit   = omit_regex,
  coef_rename = coef_rename,
  gof_omit    = "AIC|BIC|Log.Lik|F|RMSE",
  title       = "Real Price: Year-Relative Effects",
  notes       = "Reference year 2018.",
  output = "flextable"
)
```

### Sale Frequency — Thesis Table
```{r echo=TRUE, message=FALSE, warning=FALSE}
modelsummary(
  list("No Game FE" = sale_models$m1, "Game FE" = sale_models$m2),
  stars       = TRUE,
  coef_omit   = omit_regex,
  coef_rename = coef_rename,
  gof_omit    = "AIC|BIC|Log.Lik|F|RMSE",
  title       = "Sale Frequency: Year-Relative Effects",
  notes       = "Reference year 2018.",
  output = "flextable"
)
```

### Discount Depth — Thesis Table
```{r echo=TRUE, message=FALSE, warning=FALSE}
modelsummary(
  list("No Game FE" = disc_models$m1, "Game FE" = disc_models$m2),
  stars       = TRUE,
  coef_omit   = omit_regex,
  coef_rename = coef_rename,
  gof_omit    = "AIC|BIC|Log.Lik|F|RMSE",
  title       = "Discount Depth: Year-Relative Effects",
  notes       = "Reference year 2018.",
  output = "flextable"
)
```

## Sample Composition Checks
### How many months of data for each category
```{r}
reg_data %>%
  group_by(game_title, ever_on_epic) %>%
  summarise(n_months = n(), .groups = "drop") %>%
  group_by(ever_on_epic) %>%
  summarise(mean_months = mean(n_months),
            median_months = median(n_months),
            n_games = n())
```

Treated games are observed for a somewhat shorter panel than controls on 
average (70 vs. 82 months), but since the treatment interaction is identified 
off the treated games while the longer panels belong to controls, 
observation-weighting doesn't tilt the estimated effect.


### Treated / Control games by year
```{r}
reg_data %>%
  group_by(year, ever_on_epic) %>%
  summarise(n_games = n_distinct(game_title), .groups = "drop") %>%
  pivot_wider(names_from = ever_on_epic, values_from = n_games,
              names_prefix = "treated_")
```

The sample grows monotonically from 128 games in 2014 to 900 in 2024 with the 
treated share rising from ~28% to ~39%, but because treated and control arms 
grow roughly symmetrically and the interaction is a within-year contrast, this 
cross-year compositional drift affects both arms comparably rather than driving 
the estimate.

