---
title: "Section 2.1 - Game-Level Analysis: Baseline Ragression"
author: "Rocky Rowell"
date: "2026-06-10"
output: pdf_document
---

***
# Description
This file is the third analysis file and the first of the game-level analysis 
(Section 2). This file only contains the baseline game-level regression model 
used in the thesis. This model takes all games that appear on both Steam and Epic 
and run a regression model to determine the effect of Epic entry. The model is run 
for four different pre/post windows (30, 60, 90, and 180 days). Although the specifics 
of the model changed frequently over the course of the project, the final model 
included time and game fixed effects.

# Notes / Important Information
- Made the decision to drop Puzzle and Rougelike due to their low
observation count (n=12 and n=15)     
- Dropped Time_Since_Release from the regression models due to the unlikelihood
of depreciation occurring in the time window. Significance of post variables do
not change.     

***
# Setup and Data Cleaning
```{r message=FALSE, warning=FALSE}
# Libraries
library(tidyverse)
library(fixest)
library(broom)
library(ggplot2)
library(flextable)
library(modelsummary)
library(stargazer)

# Data
data <- read_csv("Data/cleaned_data.csv")
```

## Find Epic Entry Date for each Game
```{r}
epic_entry_dates <- data %>%
  filter(shop_name == "Epic") %>%
  group_by(game_title) %>%
  # entry date = first date the game appears on Epic
  summarise(entry_date = min(date), .groups = "drop")
```

## Genre columns and window vector
```{r}
genre_cols <- c("RPG","Action","Adventure","Shooter","Strategy","Simulation",
                "Platformer","Horror","OpenWorld","Survival"
                ,"Multiplayer","Narrative")

# the four pre/post windows used throughout this file
windows <- c(30, 60, 90, 180)

# the widest window we ever need; build the panel once at this width and
# subset to narrower windows on demand (avoids rebuilding the panel 4x)
max_window <- max(windows)
```

## Build Steam panel at the widest window
```{r}
steam_panel <- data %>%
  filter(shop_name == "Steam") %>%
  left_join(epic_entry_dates, by = "game_title") %>%
  mutate(
    days_since_entry = as.numeric(date - entry_date),
    ever_treated     = !is.na(entry_date),
    post             = if_else(ever_treated, days_since_entry >= 0, FALSE)
  ) %>%
  filter(!ever_treated | abs(days_since_entry) <= max_window) %>%
  group_by(game_title, date) %>%
  summarise(
    price            = mean(price, na.rm = TRUE),
    discount_percent = mean(discount_percent, na.rm = TRUE),
    entry_date       = first(entry_date),
    release_date     = first(release_date),
    days_since_entry = first(days_since_entry),
    ever_treated     = first(ever_treated),
    post             = first(post),
    across(all_of(genre_cols), first),
    sale             = first(sale),
    .groups          = "drop"
  )
```

## Clean up Loose Ends
Some games caused issues due to lack of price variation or other issues.
```{r}
# Book of Demons: convert sub-$5 records to 4.99
steam_panel <- steam_panel %>%
  mutate(price = if_else(game_title == "Book of Demons" & price < 5, 4.99, price))

# drop problematic titles
steam_panel <- steam_panel %>%
  filter(!game_title %in% c("Dying Light", "Grounded", "The Sims 4"))
```

## Add Analysis Variables (treated games only)
```{r}
treated_panel <- steam_panel %>%
  filter(ever_treated) %>%
  mutate(
    on_epic            = as.integer(days_since_entry >= 0),
    time_since_release = as.numeric(date - release_date),
    period             = if_else(days_since_entry < 0, "pre", "post"),
    cal_week           = as.integer(floor(as.numeric(date - min(date)) / 7))
  )

cat("Treated games (180-day panel):", n_distinct(treated_panel$game_title), "\n")
```


***
# Regression Analysis
Similar to Section 1's regression model, I included different variations (no game 
FE) of the regression models in the code despite not using them in the thesis.

## 1. Helper: run base + genre regression for one outcome at one window
```{r}
genre_inter <- paste0("on_epic:", genre_cols, collapse = " + ")

run_regs <- function(df, outcome_col, w) {
  d <- df %>% filter(abs(days_since_entry) <= w)

  base <- feols(
    as.formula(paste(outcome_col,
                     "~ on_epic | game_title + cal_week")),
    data = d, cluster = ~ game_title
  )

  genre <- feols(
    as.formula(paste(outcome_col,
                     "~ on_epic +", genre_inter,
                     "| game_title + cal_week")),
    data = d, cluster = ~ game_title
  )

  list(base = base, genre = genre)
}
```

## 2. Price regressions across windows
```{r message=FALSE, warning=FALSE}
price_models <- map(windows, ~ run_regs(treated_panel, "price", .x))
names(price_models) <- paste0("w", windows)

# Base Model
etable(map(price_models, "base"),
       headers = paste0(windows, "d"),
       title  = "Price ~ on_epic (base) across windows")
```

```{r}
# Genre Model
etable(map(price_models, "genre"),
       headers = paste0(windows, "d"),
       title  = "Price ~ on_epic + genres across windows")
```

## 3. Sale-frequency regressions across windows
```{r}
sale_models <- map(windows, ~ run_regs(treated_panel, "sale", .x))
names(sale_models) <- paste0("w", windows)

etable(map(sale_models, "base"),
       headers = paste0(windows, "d"),
       title  = "Sale ~ on_epic (base) across windows")
```

```{r}
etable(map(sale_models, "genre"),
       headers = paste0(windows, "d"),
       title  = "Sale ~ on_epic + genres across windows")
```

## 4. Discount-depth regressions across windows
```{r}
disc_models <- map(windows, ~ run_regs(treated_panel, "discount_percent", .x))
names(disc_models) <- paste0("w", windows)

etable(map(disc_models, "base"),
       headers = paste0(windows, "d"),
       title  = "Discount % ~ on_epic (base) across windows")
```

```{r}
etable(map(disc_models, "genre"),
       headers = paste0(windows, "d"),
       title  = "Discount % ~ on_epic + genres across windows")
```

## 5. Persistence figure: on_epic coefficient vs window length
```{r fig.width=8, fig.height=5}
collect_on_epic <- function(models, label) {
  map_dfr(names(models), function(nm) {
    m <- models[[nm]]$base
    ct <- tidy(m) %>% filter(term == "on_epic")
    tibble(
      outcome = label,
      window  = as.integer(str_remove(nm, "w")),
      estimate = ct$estimate,
      se       = ct$std.error
    )
  })
}

persistence <- bind_rows(
  collect_on_epic(price_models, "Price"),
  collect_on_epic(sale_models,  "Sale Frequency"),
  collect_on_epic(disc_models,  "Discount Depth")
)

ggplot(persistence, aes(x = window, y = estimate)) +
  geom_ribbon(aes(ymin = estimate - 1.96 * se,
                  ymax = estimate + 1.96 * se),
              alpha = 0.2, fill = "steelblue") +
  geom_line(color = "steelblue", linewidth = 0.8) +
  geom_point(size = 2, color = "steelblue") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray40") +
  facet_wrap(~ outcome, scales = "free_y") +
  scale_x_continuous(breaks = windows) +
  labs(
    title    = "Epic-Entry Effect by Window Length (base specifications)",
    subtitle = "on_epic coefficient with 95% CI | treated games only",
    x        = "Window length (days pre/post)",
    y        = "on_epic coefficient"
  ) +
  theme_minimal()
```


***
# Clean Regression Output
Like Section 1, I needed to make sure that my regression output could be used in 
actual thesis. These are just the Word outputs for the regression models.

```{r}
genre_price <- map(price_models, "genre")
genre_sale  <- map(sale_models,  "genre")
genre_disc  <- map(disc_models,  "genre")
names(genre_price) <- names(genre_sale) <- names(genre_disc) <-
  paste0(windows, "d")

make_genre_table <- function(mods, caption) {
  modelsummary(
    mods,
    coef_map = c("on_epic" = "On Epic (post-entry)"),
    gof_omit = "AIC|BIC|Log.Lik.|RMSE|Std.Errors",
    stars    = c('*' = .05, '**' = .01, '***' = .001),
    title    = caption,
    notes    = paste("Genre x on_epic interactions estimated but omitted",
                     "from display. FE: game + calendar week.",
                     "SEs clustered by game."),
    output   = "flextable"
  ) %>%
    flextable::autofit()
}

price_genre_ft <- make_genre_table(genre_price,
  "Price ~ on_epic (genre-interacted spec; genres omitted)")
sale_genre_ft  <- make_genre_table(genre_sale,
  "Sale frequency ~ on_epic (genre-interacted spec; genres omitted)")
disc_genre_ft  <- make_genre_table(genre_disc,
  "Discount depth ~ on_epic (genre-interacted spec; genres omitted)")

price_genre_ft
sale_genre_ft
disc_genre_ft
save_as_docx(price_genre_ft, sale_genre_ft, disc_genre_ft,
             path = "Output/tab_genre_regs.docx")
```

```{r}
base_price <- map(price_models, "base")
base_sale  <- map(sale_models,  "base")
base_disc  <- map(disc_models,  "base")

# window labels straight off the model lists (length-safe): "30d","60d",...
lab <- paste0(sub("^w", "", names(price_models)), "d")
names(base_price) <- names(base_sale) <- names(base_disc) <- lab

make_base_table <- function(mods, caption) {
  modelsummary(
    mods,
    coef_map = c("on_epic" = "On Epic (post-entry)"),
    gof_omit = "^R2$|R2 Adj\\.|R2 Within Adj\\.|AIC|BIC|Log\\.Lik\\.|RMSE|Std\\.Errors|FE:",
    stars    = c('*' = .05, '**' = .01, '***' = .001),
    title    = caption,
    output   = "flextable"
  ) %>%
    flextable::autofit()
}

price_base_ft <- make_base_table(base_price, "Price ~ On_Epic")
sale_base_ft  <- make_base_table(base_sale,  "Sale Frequency ~ On_Epic")
disc_base_ft  <- make_base_table(base_disc,  "Discount Depth ~ On_Epic")

price_base_ft; sale_base_ft; disc_base_ft
save_as_docx(price_base_ft, sale_base_ft, disc_base_ft,
             path = "Output/tab_base_regs.docx")
```


***
# Extra Information and Code
## Sample Diagnostics
```{r}
steam_panel %>%
  filter(ever_treated) %>%        # or remove this to check all games
  distinct(game_title, .keep_all = TRUE) %>%
  summarise(across(all_of(genre_cols), sum, na.rm = TRUE)) %>%
  pivot_longer(everything(), names_to = "genre", values_to = "n_games") %>%
  arrange(desc(n_games))
```

```{r}
steam_panel %>%
  distinct(game_title, ever_treated, .keep_all = TRUE) %>%
  group_by(ever_treated) %>%
  summarise(across(all_of(genre_cols), sum, na.rm = TRUE)) %>%
  pivot_longer(-ever_treated, names_to = "genre", values_to = "n_games") %>%
  pivot_wider(names_from = ever_treated, values_from = n_games,
              names_prefix = "treated_") %>%
  mutate(ratio = round(treated_FALSE / treated_TRUE, 1)) %>%
  arrange(ratio)
```

## T-Test Analysis
Originally, I had also included a t-test analysis of the outcome variables that 
compared the Pre-Epic Steam data to the Post-Epic Steam data for each outcome 
variable. To display these results, I created graphs that plotted the values of
each t-test in ascending order.

### 1. Helper: run per-game t-tests for one outcome at one window
```{r echo=TRUE}
# outcome_col: name of the column to test ("price", "sale", "discount_percent")
# w:           window length in days
run_ttests <- function(df, outcome_col, w, label) {
  df %>%
    filter(abs(days_since_entry) <= w) %>%
    group_by(game_title) %>%
    filter(sum(period == "pre") >= 5, sum(period == "post") >= 5) %>%
    group_modify(~ {
      pre  <- .x[[outcome_col]][.x$period == "pre"]
      post <- .x[[outcome_col]][.x$period == "post"]
      if (sd(pre) == 0 && sd(post) == 0) return(tibble())
      tidy(t.test(post, pre, alternative = "two.sided"))
    }) %>%
    ungroup() %>%
    mutate(
      outcome      = label,
      window       = w,
      significant  = p.value < 0.05,
      direction_up = estimate > 0
    )
}
```

### 2. Run all outcomes across all windows
```{r echo=TRUE}
outcome_specs <- tibble(
  col   = c("price", "sale", "discount_percent"),
  label = c("Price", "Sale Frequency", "Discount Depth")
)

# run t-tests (flat games excluded inside helper) 
ttest_results <- map_dfr(windows, function(w) {
  map_dfr(seq_len(nrow(outcome_specs)), function(j) {
    run_ttests(treated_panel, outcome_specs$col[j], w, outcome_specs$label[j])
  })
}) %>%
  mutate(no_change = FALSE)

# identify flat games for every outcome + window combination 
flat_games <- map_dfr(windows, function(w) {
  map_dfr(seq_len(nrow(outcome_specs)), function(j) {
    col   <- outcome_specs$col[j]
    label <- outcome_specs$label[j]

    treated_panel %>%
      filter(abs(days_since_entry) <= w) %>%
      group_by(game_title) %>%
      filter(sum(period == "pre") >= 5, sum(period == "post") >= 5) %>%
      summarise(
        pre_sd  = sd(.data[[col]][period == "pre"],  na.rm = TRUE),
        post_sd = sd(.data[[col]][period == "post"], na.rm = TRUE),
        .groups = "drop"
      ) %>%
      filter(pre_sd == 0 & post_sd == 0) %>%
      mutate(
        estimate     = 0,
        p.value      = 1,
        significant  = FALSE,
        direction_up = FALSE,
        no_change    = TRUE,
        outcome      = label,
        window       = w
      ) %>%
      select(game_title, estimate, p.value, significant,
             direction_up, no_change, outcome, window)
  })
})

# bind together 
ttest_results <- bind_rows(ttest_results, flat_games)

# sanity check 
ttest_results %>%
  count(outcome, window, no_change) %>%
  pivot_wider(names_from = no_change, values_from = n,
              names_prefix = "no_change_") %>%
  arrange(outcome, window)
```

### 3. Plot helper: one t-test scatter for a given outcome + window
```{r echo=TRUE}
plot_ttests <- function(res, outcome_label, w, y_lab) {
  d <- res %>%
    filter(outcome == outcome_label, window == w) %>%
    arrange(estimate) %>%
    mutate(
      game_index  = row_number(),
      color_group = case_when(
        no_change                        ~ "No change",
        direction_up  & significant      ~ "Rose (p<0.05)",
        !direction_up & significant      ~ "Fell (p<0.05)",
        direction_up  & !significant     ~ "Rose (n.s.)",
        !direction_up & !significant     ~ "Fell (n.s.)"
      )
    )

  ggplot(d, aes(x = game_index, y = estimate)) +
    geom_point(aes(color = color_group), size = 2) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray40") +
    scale_color_manual(
      values = c(
        "No change"     = "gray60",
        "Fell (n.s.)"   = "#93c4df",
        "Rose (n.s.)"   = "#f4a582",
        "Fell (p<0.05)" = "steelblue",
        "Rose (p<0.05)" = "firebrick"
      ),
      name = NULL,
      drop = FALSE
    ) +
    labs(
      x        = "Games (sorted by change)",
      y        = y_lab,
      title    = paste0(outcome_label, " Change Within ", w,
                        " Days of Epic Entry"),
      subtitle = paste0("Each point = one game | n = ", nrow(d), " games")
    ) +
    theme_minimal() +
    theme(legend.position = "bottom")
}
```

### 4. Price t-test plots (one per window)
```{r fig.width=8, fig.height=5, echo=TRUE}
for (w in windows) {
  print(plot_ttests(ttest_results, "Price", w,
                    "Mean price change after Epic entry (USD)"))
}
```

### 5. Sale-frequency t-test plots (one per window)
```{r fig.width=8, fig.height=5, echo=TRUE}
for (w in windows) {
  print(plot_ttests(ttest_results, "Sale Frequency", w,
                    "Mean change in sale frequency after Epic entry"))
}
```

### 6. Discount-depth t-test plots (one per window)
```{r fig.width=8, fig.height=5, echo=TRUE}
for (w in windows) {
  print(plot_ttests(ttest_results, "Discount Depth", w,
                    "Mean change in discount percent after Epic entry"))
}
```

### 7. Summary counts across all outcomes and windows
```{r echo=TRUE}
ttest_results %>%
  group_by(outcome, window) %>%
  summarise(
    n_games    = n(),
    n_rose     = sum(direction_up),
    n_fell     = sum(!direction_up),
    n_sig_rose = sum(direction_up & significant),
    n_sig_fell = sum(!direction_up & significant),
    .groups = "drop"
  ) %>%
  arrange(outcome, window)
```

```{r echo=TRUE}
ttest_summary <- ttest_results %>%
  group_by(outcome, window) %>%
  summarise(
    n_rose     = sum(direction_up),
    n_fell     = sum(!direction_up),
    n_sig_rose = sum(direction_up & significant),
    n_sig_fell = sum(!direction_up & significant),
    .groups = "drop"
  ) %>%
  mutate(outcome = factor(outcome,
    levels = c("Price", "Sale Frequency", "Discount Depth"))) %>%
  arrange(outcome, window)

ttest_ft <- ttest_summary %>%
  flextable() %>%
  set_header_labels(
    outcome    = "Outcome",
    window     = "Window (days)",
    n_rose     = "Rose",
    n_fell     = "Fell",
    n_sig_rose = "Rose (p<0.05)",
    n_sig_fell = "Fell (p<0.05)"
  ) %>%
  merge_v(j = "outcome") %>%
  valign(j = "outcome", valign = "top") %>%
  theme_booktabs() %>%
  align(j = 2:6, align = "center", part = "all") %>%
  align(j = "outcome", align = "left", part = "all") %>%
  autofit() %>%
  fix_border_issues()

ttest_ft
save_as_docx(ttest_ft, path = "Output/tab_ttest_summary.docx")
```

```{r echo=TRUE}
ttest_summary_df <- ttest_summary %>%
  mutate(outcome = as.character(outcome)) %>%
  as.data.frame()

stargazer(
  ttest_summary_df,
  summary  = FALSE,
  rownames = FALSE,
  type     = "latex",   # "html" to open in Word, "latex" for a PDF build
  digits   = 0,
  title    = "T-Test Outcomes",
  covariate.labels = c("Outcome", " Window (days) ",
                       " Rose ", " Fell ", " Rose (p<0.05) ", " Fell (p<0.05) "),
  out = "Output/tab_ttest_summary.html"
)
#For Word: type = "html", out = "Output/tab_ttest_summary.html"
```
