---
title: "Section 2.2 - Game-Level Analysis: Stacked DiD and Synthetic Control DiD"
author: "Rocky Rowell"
date: "2026-06-30"
output: pdf_document
---

***
# Description
This is the fourth and final analysis file for the project. It builds the two
difference-in-differences models used in the thesis. Both designs add a control
group, which is what the baseline model in Section 2.1 lacks. The first is a
stacked DiD, where each treated game is paired with one matched Steam-Only
control. The second is a synthetic control DiD, where each treated game is
paired with a weighted combination of Steam-Only donor games, followed by a
pooled DiD across the treated-synthetic pairs. Both are estimated at 60, 90,
and 180 days around each game's Epic entry date.

These models gave me the most trouble of anything in the project, so this file
carries far more diagnostic code than the other analysis files. I opted to keep 
these code snippets included.

# Notes / Important Information
- Like all other sections, outcomes are price, sale frequency, and discount depth. 
A fourth outcome, discount depth conditional on a sale being active, is estimated 
as an exploratory check and does not appear in the thesis.
- Discount depth averages in zeros on non-sale days, so it is close to the
product of sale frequency and conditional depth. The conditional measure
separates discounting more often from discounting more deeply.
- The 30-day window used in Section 2.1 is dropped here. At weekly aggregation
it leaves only four pre-treatment weeks, which is too thin to fit a trajectory
against.
- Synthetic control weights are solved exactly with quadratic programming. An
earlier version used hand-written gradient descent that was silently returning
something close to the uniform donor average. The Extra section at the back
documents how I found this and confirms the replacement works.
- Matching is done with replacement, so a Steam-Only game can serve as the
control for more than one treated game. Section 4.7 reports how often this
happens.
- Weights and matches are fitted separately for each outcome rather than being
fitted on price and reused.

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

***
# 0. Setup
## 0.1 Libraries
```{r}
library(tidyverse)
library(fixest)
library(broom)
library(ggplot2)
library(modelsummary)
library(quadprog) 
library(MASS, include.only = "ginv")
library(flextable)
library(officer)
select <- dplyr::select   # MASS masks select()
```

## 0.2 Load Data
```{r}
data <- read_csv("Data/cleaned_data.csv")
```

## 0.3 Epic Entry Dates
```{r}
epic_entry_dates <- data %>%
  filter(shop_name == "Epic") %>%
  group_by(game_title) %>%
  summarise(entry_date = min(date), .groups = "drop")
```

## 0.4 Globals
Each outcome is listed alongside the outcome its controls are matched on and
whether it is a primary result. Conditional discount depth is undefined in
weeks with no sale days, which makes it too sparse to match on directly, so it
borrows the discount depth match.
```{r}
genre_cols <- c("RPG","Action","Adventure","Shooter","Strategy","Simulation",
                "Platformer","Puzzle","Horror","OpenWorld","Survival",
                "Roguelike","Multiplayer","Narrative")

# Every outcome, the outcome its controls are matched on, and whether it is primary.
# disc_cond is too sparse (undefined in weeks with no sale days) to match on
# directly, so it borrows the discount-depth match.
outcome_spec <- tibble::tribble(
  ~col,        ~label,                           ~match_on,  ~primary,
  "price",     "Price (USD)",                    "price",    TRUE,
  "sale",      "Sale Frequency",                 "sale",     TRUE,
  "disc",      "Discount Depth (%)",             "disc",     TRUE,
  "disc_cond", "Conditional Discount Depth (%)", "disc",     FALSE
)
outcome_cols   <- outcome_spec$col
outcome_labels <- outcome_spec$label
match_keys     <- unique(outcome_spec$match_on)

# Analysis windows. 30d is dropped: at weekly aggregation it yields
# floor(30/7) = 4 pre-treatment weeks, and min_pre_weeks = max(4, .) requires 4,
# so every pre-week must be present. Too thin to fit trajectories.
windows <- c(60, 90, 180)

# Panel half-width. Set to 2 x the widest analysis window so the in-time placebo
# (fake entry at true_entry - w) has pre-fake-entry data to match on.
panel_halfwidth <- 2 * max(windows)
```

***
# 1. Panel Construction
## 1.1 Build the Steam Panel
```{r}
steam_raw <- data %>%
  filter(shop_name == "Steam") %>%
  left_join(epic_entry_dates, by = "game_title") %>%
  mutate(
    days_since_entry = as.numeric(date - entry_date),
    ever_treated     = !is.na(entry_date),
    post             = if_else(ever_treated, days_since_entry >= 0, FALSE)
  ) %>%
  filter(!ever_treated | abs(days_since_entry) <= panel_halfwidth)

steam_panel <- steam_raw %>%
  group_by(game_title, date) %>%
  summarise(
    price            = mean(price,            na.rm = TRUE),
    sale             = mean(sale,             na.rm = TRUE),
    disc             = mean(discount_percent, na.rm = TRUE),
    # Conditional depth: mean discount on days the game IS on sale.
    # NaN when the game had no sale rows that day; converted to NA below.
    disc_cond        = mean(discount_percent[sale == 1], na.rm = TRUE),
    entry_date       = first(entry_date),
    release_date     = first(release_date),
    days_since_entry = first(days_since_entry),
    ever_treated     = first(ever_treated),
    post             = first(post),
    across(all_of(genre_cols), first),
    .groups          = "drop"
  ) %>%
  mutate(across(all_of(outcome_cols), ~ if_else(is.nan(.x), NA_real_, .x)))
```

## 1.2 Trim Controls to the Treated Calendar Range
```{r}
window_min <- steam_panel %>% filter(ever_treated) %>% summarise(m = min(date)) %>% pull(m)
window_max <- steam_panel %>% filter(ever_treated) %>% summarise(m = max(date)) %>% pull(m)

steam_panel <- steam_panel %>%
  filter(ever_treated | (date >= window_min & date <= window_max))
```

## 1.3 Data Corrections
Two hand corrections are applied before any analysis. Both are recorded here
rather than in the cleaning file, since undocumented exclusions read as
researcher degrees of freedom even when they are entirely legitimate.
```{r}
# CORRECTION - Book of Demons.
# IsThereAnyDeal recorded a small number of sub-$5 observations for this title
# on dates when the Steam store page listed $4.99. These are recording errors
# rather than real price movements, so they are reset to the listed price.
steam_panel <- steam_panel %>%
  mutate(price = if_else(game_title == "Book of Demons" & price < 5, 4.99, price))

# EXCLUSIONS - three titles whose base-price series is not comparable across
# the entry window.
#   The Sims 4  - converted to free-to-play in October 2022, so the base price
#                 outcome is undefined for much of the window.
#   Dying Light - TODO: record reason before publishing.
#   Grounded    - TODO: record reason before publishing.
dropped_titles <- c("Dying Light", "Grounded", "The Sims 4")
steam_panel <- steam_panel %>% filter(!game_title %in% dropped_titles)
```

## 1.4 Sample Flow
Tracks how many games survive each stage, from the raw pull down to the treated
sample and the Steam-Only control pool. Retention into each individual DiD
window is reported separately in Sections 4.5 and 5.5.
```{r}
sample_flow <- tibble::tribble(
  ~stage,                                   ~n_games,
  "All games in raw data",                   n_distinct(data$game_title),
  "Ever listed on Epic (Dual-Platform)",     n_distinct(epic_entry_dates$game_title),
  "After hand exclusions",                   n_distinct(steam_panel$game_title[steam_panel$ever_treated]),
  "Steam-Only (control pool)",               n_distinct(steam_panel$game_title[!steam_panel$ever_treated])
)
sample_flow
```

***
# 2. Shared Matching Objects
Both estimators draw on the same donor pool and the same weekly series, so those
objects are built once here. Genres are converted to a matrix so that donor
eligibility can be checked with a single matrix multiply.
```{r}
origin <- min(steam_panel$date)

game_attrs <- data %>%
  group_by(game_title) %>%
  summarise(release_date = first(release_date),
            across(all_of(genre_cols), first), .groups = "drop")

treated_info <- steam_panel %>%
  filter(ever_treated) %>%
  distinct(game_title, entry_date) %>%
  left_join(game_attrs, by = "game_title")

entry_lookup <- setNames(treated_info$entry_date, treated_info$game_title)

control_ranges <- steam_panel %>%
  filter(!ever_treated) %>%
  group_by(game_title) %>%
  summarise(min_date = min(date), max_date = max(date), .groups = "drop") %>%
  left_join(game_attrs, by = "game_title")

control_genre_mat <- control_ranges %>% select(all_of(genre_cols)) %>% as.matrix()

# Weekly calendar series for ALL outcomes (treated + control)
to_weekly <- function(df) {
  df %>%
    mutate(cal_week = as.integer(floor(as.numeric(date - origin) / 7))) %>%
    group_by(game_title, cal_week) %>%
    summarise(across(all_of(outcome_cols), ~ mean(.x, na.rm = TRUE)), .groups = "drop") %>%
    mutate(across(all_of(outcome_cols), ~ if_else(is.nan(.x), NA_real_, .x)))
}

treated_weekly_cal <- steam_panel %>% filter(ever_treated)  %>% to_weekly()
control_weekly_cal <- steam_panel %>% filter(!ever_treated) %>% to_weekly()
```

***
# 3. Weight Solver
Solves the constrained least-squares problem for the synthetic control weights,
subject to the weights being non-negative and summing to one. With demeaning
turned on, the fit targets the treated game's trend rather than its level, since
the level gap is absorbed by the sub-experiment fixed effects anyway.

This replaced a hand-written gradient descent routine that was not converging.
The diagnostic that caught it, along with the old solver itself, is kept in the
Extra section at the back of this file.
```{r}
solve_synth_weights <- function(Y_pre, X_pre, demean = TRUE, ridge = 1e-6) {
  X_pre <- as.matrix(X_pre)
  J <- ncol(X_pre)
  if (J < 1) return(numeric(0))
  if (J == 1) return(1)

  if (demean) {
    Yc <- Y_pre - mean(Y_pre)
    Xc <- sweep(X_pre, 2, colMeans(X_pre), "-")
  } else {
    Yc <- Y_pre
    Xc <- X_pre
  }

  Dmat0 <- crossprod(Xc)
  dvec  <- as.vector(crossprod(Xc, Yc))
  Amat  <- cbind(rep(1, J), diag(J))   # col 1: sum(w) = 1 (equality); rest: w >= 0
  bvec  <- c(1, rep(0, J))
  scale_d <- max(mean(diag(Dmat0)), 1e-8)

  # X'X is singular whenever J > T_pre, so escalate the ridge until PD.
  for (mult in c(1, 10, 100, 1e3, 1e4, 1e5, 1e6)) {
    Dmat <- Dmat0 + diag(ridge * mult * scale_d, J)
    sol <- tryCatch(quadprog::solve.QP(Dmat, dvec, Amat, bvec, meq = 1),
                    error = function(e) NULL)
    if (!is.null(sol)) {
      w <- pmax(sol$solution, 0)
      s <- sum(w)
      if (s > 0) return(w / s)
    }
  }
  rep(1 / J, J)   # last-resort fallback (should not trigger)
}
```

***
# 4. Stacked Difference-in-Differences
## 4.1 Matcher
Each treated game is paired with the single Steam-Only game that best matches
it. Trajectory distance is computed on demeaned series so it captures trend
divergence, which is what the game fixed effects do not absorb. The level gap,
genre overlap, and release-date distance enter as separate, lower-weighted
criteria.
```{r}
# Level is a SEPARATE, lower-weighted criterion; trajectory distance is
# computed on demeaned series so it captures TREND divergence, which is what the
# subexp^game_title FE does NOT absorb.
match_w <- c(traj = 1.0, level = 0.3, genre = 0.3, release = 0.1)

safe_z <- function(x) {
  s <- sd(x, na.rm = TRUE)
  if (is.na(s) || s == 0) return(rep(0, length(x)))
  (x - mean(x, na.rm = TRUE)) / s
}

match_controls <- function(w, n_pre_weeks, outcome = "price",
                           entry_map = entry_lookup,
                           games = treated_info$game_title) {
  min_overlap   <- 1
  min_pre_weeks <- max(4, floor(n_pre_weeks / 2))

  map_dfr(games, function(tg) {
    tr        <- treated_info %>% filter(game_title == tg)
    E         <- entry_map[[tg]]
    entry_cal <- as.integer(floor(as.numeric(E - origin) / 7))
    pre_weeks <- (entry_cal - n_pre_weeks):(entry_cal - 1)
    tr_genres <- tr %>% select(all_of(genre_cols)) %>% unlist()

    t_path <- treated_weekly_cal %>%
      filter(game_title == tg, cal_week %in% pre_weeks) %>%
      transmute(cal_week, t_val = .data[[outcome]]) %>%
      filter(!is.na(t_val))
    if (nrow(t_path) < min_pre_weeks) return(NULL)

    shared <- as.integer(control_genre_mat %*% tr_genres)
    elig <- control_ranges %>%
      mutate(shared_genres = shared) %>%
      filter(shared_genres >= min_overlap,
             min_date <= E - w, max_date >= E + w)
    if (nrow(elig) == 0) return(NULL)

    cand <- control_weekly_cal %>%
      filter(game_title %in% elig$game_title, cal_week %in% pre_weeks) %>%
      transmute(game_title, cal_week, c_val = .data[[outcome]]) %>%
      filter(!is.na(c_val)) %>%
      inner_join(t_path, by = "cal_week") %>%
      group_by(game_title) %>%
      summarise(
        n_overlap = n(),
        # TREND distance (both series demeaned over the overlapping weeks)
        traj_mse  = mean(((c_val - mean(c_val)) - (t_val - mean(t_val)))^2),
        # LEVEL gap, kept separate and down-weighted
        level_gap = abs(mean(c_val) - mean(t_val)),
        .groups   = "drop"
      ) %>%
      filter(n_overlap >= min_pre_weeks) %>%
      left_join(elig %>% select(game_title, shared_genres, release_date),
                by = "game_title")
    if (nrow(cand) == 0) return(NULL)

    cand <- cand %>%
      mutate(
        z_traj  =  safe_z(traj_mse),
        z_level =  safe_z(level_gap),
        z_genre = -safe_z(shared_genres),
        z_rel   =  safe_z(abs(as.numeric(release_date) - as.numeric(tr$release_date))),
        score   = match_w["traj"]    * z_traj +
                  match_w["level"]   * z_level +
                  match_w["genre"]   * z_genre +
                  match_w["release"] * z_rel
      )

    best <- cand %>% slice_min(score, n = 1, with_ties = FALSE)
    tibble(
      treated_game  = tg,
      control_game  = best$game_title,
      traj_rmse     = sqrt(best$traj_mse),   # TREND rmse — comparable to synth pre_rmse_trend
      level_gap     = best$level_gap,
      shared_genres = best$shared_genres,
      n_pre_overlap = best$n_overlap,
      n_eligible    = nrow(cand)
    )
  })
}
```

## 4.2 Stacked Panel Builder
```{r}
build_stacked <- function(matched, w, entry_map = entry_lookup) {
  n_weeks <- floor(w / 7)
  if (is.null(matched) || nrow(matched) == 0) return(NULL)

  map_dfr(seq_len(nrow(matched)), function(i) {
    tg    <- matched$treated_game[i]
    cg    <- matched$control_game[i]
    entry <- entry_map[[tg]]

    t_rows <- steam_panel %>%
      filter(game_title == tg,
             date >= entry - w, date <= entry + w) %>%
      transmute(subexp = tg, game_title, treated = 1L,
                across(all_of(outcome_cols)),
                days_since_entry = as.numeric(date - entry))

    c_rows <- steam_panel %>%
      filter(game_title == cg, date >= entry - w, date <= entry + w) %>%
      transmute(subexp = tg, game_title, treated = 0L,
                across(all_of(outcome_cols)),
                days_since_entry = as.numeric(date - entry))

    bind_rows(t_rows, c_rows)
  }) %>%
    mutate(event_week = days_since_entry %/% 7) %>%
    filter(event_week >= -n_weeks, event_week <= n_weeks) %>%
    group_by(subexp, game_title, treated, event_week) %>%
    summarise(across(all_of(outcome_cols), ~ mean(.x, na.rm = TRUE)), .groups = "drop") %>%
    mutate(across(all_of(outcome_cols), ~ if_else(is.nan(.x), NA_real_, .x)),
           post = as.integer(event_week >= 0))
}
```

## 4.3 Model Runner and Joint Pre-Trend Test
The pre-trend test is a Wald chi-square on the joint nullity of every
pre-period lead. A high p-value converts "the event study plot looks flat" into
"parallel pre-trends are not rejected".
```{r}
# Wald chi-square on the joint nullity of ALL pre-period leads.
pretrend_test <- function(es) {
  nm  <- names(coef(es))
  pre <- nm[grepl("event_week::-", nm)]
  if (!length(pre)) return(tibble(chi2 = NA_real_, df = NA_integer_, p_value = NA_real_))
  b  <- coef(es)[pre]
  V  <- vcov(es)[pre, pre, drop = FALSE]
  Vi <- tryCatch(solve(V), error = function(e) MASS::ginv(V))
  chi2 <- as.numeric(t(b) %*% Vi %*% b)
  tibble(chi2 = chi2, df = length(pre),
         p_value = pchisq(chi2, df = length(pre), lower.tail = FALSE))
}

run_one_stacked <- function(dat, oc) {
  fe  <- "subexp^game_title + subexp^event_week"
  att <- feols(as.formula(paste0(oc, " ~ treated:post | ", fe)),
               data = dat, cluster = ~ game_title)
  es  <- feols(as.formula(paste0(oc, " ~ i(event_week, treated, ref = -1) | ", fe)),
               data = dat, cluster = ~ game_title)
  list(att = att, es = es, pretrend = pretrend_test(es))
}
```

## 4.4 Run
```{r}
did_results <- map(windows, function(w) {
  n_pre <- floor(w / 7)

  matched <- map(setNames(match_keys, match_keys), ~ match_controls(w, n_pre, .x))
  stacked <- map(matched, ~ build_stacked(.x, w))

  models <- map(setNames(outcome_cols, outcome_cols), function(oc) {
    key <- outcome_spec$match_on[outcome_spec$col == oc]
    run_one_stacked(stacked[[key]], oc)
  })

  list(window = w, matched = matched, stacked = stacked, models = models)
})
names(did_results) <- paste0("w", windows)
```

## 4.5 Match Quality
Trajectory RMSE here is measured on demeaned series, which makes it directly
comparable to the synthetic control's pre-period trend RMSE in Section 5.5.
```{r}
stacked_quality <- map_dfr(did_results, function(r) {
  map_dfr(match_keys, function(k) {
    m <- r$matched[[k]]
    tibble(
      window          = r$window,
      matched_on      = k,
      n_matched       = nrow(m),
      mean_traj_rmse  = round(mean(m$traj_rmse,  na.rm = TRUE), 3),  # TREND rmse
      median_traj_rmse= round(median(m$traj_rmse, na.rm = TRUE), 3),
      mean_level_gap  = round(mean(m$level_gap,  na.rm = TRUE), 3),
      mean_shared     = round(mean(m$shared_genres), 2),
      mean_n_eligible = round(mean(m$n_eligible), 1)
    )
  })
})
stacked_quality
```

## 4.6 Covariate Balance, Treated vs. Matched Control
```{r}
balance_table <- map_dfr(did_results, function(r) {
  map_dfr(match_keys, function(k) {
    m <- r$matched[[k]]
    if (is.null(m) || nrow(m) == 0) return(NULL)

    # Iterate ROW-WISE so a control reused across sub-experiments is evaluated on
    # the correct treated game's pre-window each time.
    pair_means <- map_dfr(seq_len(nrow(m)), function(i) {
      E <- entry_lookup[[m$treated_game[i]]]
      tw <- steam_panel %>%
        filter(game_title == m$treated_game[i], date >= E - r$window, date < E) %>%
        summarise(across(all_of(outcome_cols), ~ mean(.x, na.rm = TRUE))) %>%
        mutate(grp = "Treated")
      cw <- steam_panel %>%
        filter(game_title == m$control_game[i], date >= E - r$window, date < E) %>%
        summarise(across(all_of(outcome_cols), ~ mean(.x, na.rm = TRUE))) %>%
        mutate(grp = "Matched control")
      bind_rows(tw, cw)
    })

    pair_means %>%
      group_by(grp) %>%
      summarise(across(all_of(outcome_cols), ~ round(mean(.x, na.rm = TRUE), 3)), .groups = "drop") %>%
      mutate(window = r$window, matched_on = k, .before = 1)
  })
})
balance_table
```

## 4.7 Control Reuse
Matching is done with replacement, so this quantifies how concentrated the
control pool ends up being.
```{r}
reuse_table <- map_dfr(did_results, function(r) {
  map_dfr(match_keys, function(k) {
    m <- r$matched[[k]]
    tab <- table(m$control_game)
    tibble(
      window           = r$window,
      matched_on       = k,
      n_treated        = nrow(m),
      n_unique_controls= length(tab),
      max_reuse        = max(tab),
      mean_reuse       = round(mean(tab), 2),
      pct_controls_used_once = round(100 * mean(tab == 1), 1)
    )
  })
})
reuse_table
```

***
# 5. Synthetic Control DiD
Each treated game is matched to a weighted combination of Steam-Only donors
fitted on its pre-entry trend, and the treated-synthetic pairs are then pooled
into a single DiD. This follows the constrained regression approach in
Doudchenko and Imbens (2016), with the simplex-constrained weights of Abadie,
Diamond and Hainmueller (2010) and pooling across treated units as in Cavallo,
Galiani, Noy and Pantano (2013). It is not the synthetic difference-in-
differences of Arkhangelsky et al. (2021), which also estimates time weights.

## 5.1 Synthetic Control Builder
```{r}
make_synth <- function(tg, w, n_weeks, fit_on = "price", apply_to = fit_on,
                       entry_map = entry_lookup) {
  tr        <- treated_info %>% filter(game_title == tg)
  E         <- entry_map[[tg]]
  entry_cal <- as.integer(floor(as.numeric(E - origin) / 7))
  tr_genres <- tr %>% select(all_of(genre_cols)) %>% unlist()

  pre_weeks  <- (entry_cal - n_weeks):(entry_cal - 1)
  full_weeks <- (entry_cal - n_weeks):(entry_cal + n_weeks)
  min_pre    <- max(4, floor(n_weeks / 2))

  t_full <- treated_weekly_cal %>%
    filter(game_title == tg, cal_week %in% full_weeks) %>%
    arrange(cal_week)
  if (nrow(t_full) == 0) return(NULL)

  y_fit_all <- t_full[[fit_on]]
  if (sum(t_full$cal_week %in% pre_weeks & !is.na(y_fit_all)) < min_pre) return(NULL)

  shared <- as.integer(control_genre_mat %*% tr_genres)
  elig <- control_ranges %>%
    mutate(shared_genres = shared) %>%
    filter(shared_genres >= 1, min_date <= E - w, max_date >= E + w) %>%
    pull(game_title)
  n_elig <- length(elig)
  if (n_elig < 3) return(NULL)

  donor_data <- control_weekly_cal %>%
    filter(game_title %in% elig, cal_week %in% full_weeks)

  # ---- donor matrix used to FIT the weights (must be complete) ----
  fit_wide <- donor_data %>%
    transmute(game_title, cal_week, value = .data[[fit_on]]) %>%
    pivot_wider(names_from = game_title, values_from = value) %>%
    arrange(cal_week)

  Xall <- fit_wide %>% select(-cal_week)
  keep <- colSums(is.na(Xall)) == 0
  n_kept <- sum(keep)
  if (n_kept < 3) return(NULL)
  donors <- names(Xall)[keep]
  Xall   <- as.matrix(Xall[, keep, drop = FALSE])

  weeks   <- fit_wide$cal_week
  t_idx   <- match(weeks, t_full$cal_week)
  Y_fit   <- y_fit_all[t_idx]
  pre_idx <- which(weeks %in% pre_weeks)
  ok      <- pre_idx[!is.na(Y_fit[pre_idx])]
  if (length(ok) < min_pre) return(NULL)

  Yp <- Y_fit[ok]
  Xp <- Xall[ok, , drop = FALSE]

  # Exact QP on DEMEANED series
  wts <- solve_synth_weights(Yp, Xp, demean = TRUE)

  fit_pre        <- as.vector(Xp %*% wts)
  pre_rmse_trend <- sqrt(mean(((fit_pre - mean(fit_pre)) - (Yp - mean(Yp)))^2))
  pre_rmse_level <- sqrt(mean((fit_pre + (mean(Yp) - mean(fit_pre)) - Yp)^2))

  # ---- apply the SAME weights to the target outcome ----
  app_wide <- donor_data %>%
    transmute(game_title, cal_week, value = .data[[apply_to]]) %>%
    pivot_wider(names_from = game_title, values_from = value) %>%
    arrange(cal_week)
  app_wide <- app_wide[match(weeks, app_wide$cal_week), , drop = FALSE]
  Aapp     <- as.matrix(app_wide[, donors, drop = FALSE])

  # NA-safe weighted mean (renormalise over donors available that week)
  synth_raw <- apply(Aapp, 1, function(rw) {
    o <- !is.na(rw)
    if (!any(o)) return(NA_real_)
    sum(rw[o] * wts[o]) / sum(wts[o])
  })

  Y_app  <- t_full[[apply_to]][t_idx]
  ok_app <- pre_idx[!is.na(Y_app[pre_idx]) & !is.na(synth_raw[pre_idx])]
  if (length(ok_app) < 2) return(NULL)

  # Restore the level using the APPLIED outcome's pre-period
  offset <- mean(Y_app[ok_app]) - mean(synth_raw[ok_app])

  tibble(
    subexp         = tg,
    cal_week       = weeks,
    event_week     = weeks - entry_cal,
    t_val          = Y_app,
    s_val          = synth_raw + offset,
    pre_rmse_trend = pre_rmse_trend,
    pre_rmse_level = pre_rmse_level,
    n_elig         = n_elig,
    n_donors       = n_kept,     # survivors of the complete-case filter
    max_weight     = max(wts),
    eff_donors     = sum(wts > 0.01)
  ) %>% filter(!is.na(t_val), !is.na(s_val))
}
```

## 5.2 Panel Assembly
```{r}
build_synth_panel <- function(w, fit_on, apply_to = fit_on, entry_map = entry_lookup,
                              games = treated_info$game_title) {
  n_weeks <- floor(w / 7)
  lst <- map(games, ~ make_synth(.x, w, n_weeks, fit_on, apply_to, entry_map))
  lst <- compact(lst)
  if (!length(lst)) return(NULL)

  panel <- map_dfr(lst, function(s) {
    bind_rows(
      s %>% transmute(subexp, event_week, treated = 1L, y = t_val),
      s %>% transmute(subexp, event_week, treated = 0L, y = s_val)
    )
  }) %>% mutate(post = as.integer(event_week >= 0))

  diag <- map_dfr(lst, ~ distinct(.x, subexp, pre_rmse_trend, pre_rmse_level,
                                  n_elig, n_donors, max_weight, eff_donors))
  list(panel = panel, diag = diag)
}
```

## 5.3 Model Runner
```{r}
run_one_synth <- function(panel) {
  fe  <- "subexp^treated + subexp^event_week"
  att <- feols(as.formula(paste0("y ~ treated:post | ", fe)),
               data = panel, cluster = ~ subexp)
  es  <- feols(as.formula(paste0("y ~ i(event_week, treated, ref = -1) | ", fe)),
               data = panel, cluster = ~ subexp)
  list(att = att, es = es, pretrend = pretrend_test(es))
}
```

## 5.4 Run
```{r}
synth_results <- map(windows, function(w) {
  by_outcome <- map(setNames(outcome_cols, outcome_cols), function(oc) {
    fo <- outcome_spec$match_on[outcome_spec$col == oc]
    sp <- build_synth_panel(w, fit_on = fo, apply_to = oc)
    if (is.null(sp)) return(NULL)
    list(models = run_one_synth(sp$panel), diag = sp$diag, panel = sp$panel)
  })
  list(window = w, by_outcome = by_outcome)
})
names(synth_results) <- paste0("w", windows)
```

## 5.5 Synthetic Control Diagnostics
```{r}
synth_quality <- map_dfr(synth_results, function(r) {
  map_dfr(outcome_cols, function(oc) {
    x <- r$by_outcome[[oc]]
    if (is.null(x)) return(NULL)
    d <- x$diag
    tibble(
      window             = r$window,
      outcome            = oc,
      fitted_on          = outcome_spec$match_on[outcome_spec$col == oc],
      n_synth            = nrow(d),
      mean_pre_rmse_trend= round(mean(d$pre_rmse_trend, na.rm = TRUE), 3),  # <- the slide number
      med_pre_rmse_trend = round(median(d$pre_rmse_trend, na.rm = TRUE), 3),
      mean_pre_rmse_level= round(mean(d$pre_rmse_level, na.rm = TRUE), 3),
      mean_n_eligible    = round(mean(d$n_elig), 1),
      mean_n_donors_kept = round(mean(d$n_donors), 1),
      pct_donors_lost    = round(100 * (1 - mean(d$n_donors / d$n_elig)), 1),
      mean_max_weight    = round(mean(d$max_weight), 3),
      mean_eff_donors    = round(mean(d$eff_donors), 1)
    )
  })
})
synth_quality
```

### Pre-Trend Fit: Stacked vs. Synthetic
The ratio compares how well each estimator tracks the treated game's
pre-treatment trend. A value above one means the synthetic control fits better
than the single matched control, which is the condition under which the
synthetic estimates are preferred. A value below one would favor the stacked
estimates.
```{r}
fit_comparison <- stacked_quality %>%
  select(window, matched_on, stacked_trend_rmse = mean_traj_rmse, n_matched) %>%
  left_join(
    synth_quality %>%
      filter(outcome == fitted_on) %>%
      select(window, matched_on = fitted_on,
             synth_trend_rmse = mean_pre_rmse_trend, n_synth),
    by = c("window", "matched_on")
  ) %>%
  mutate(synth_better_by = round(stacked_trend_rmse / synth_trend_rmse, 2))
fit_comparison
```

***
# 6. Results
## 6.1 Pooled ATT
```{r}
comparison <- bind_rows(
  map_dfr(did_results, function(r) {
    map_dfr(outcome_cols, function(oc) {
      tidy(r$models[[oc]]$att) %>%
        filter(term == "treated:post") %>%
        transmute(method = "Stacked DiD", outcome = oc, window = r$window,
                  estimate, std.error, statistic, p.value,
                  n_obs = nobs(r$models[[oc]]$att))
    })
  }),
  map_dfr(synth_results, function(r) {
    map_dfr(outcome_cols, function(oc) {
      x <- r$by_outcome[[oc]]
      if (is.null(x)) return(NULL)
      tidy(x$models$att) %>%
        filter(term == "treated:post") %>%
        transmute(method = "Synthetic Control DiD", outcome = oc, window = r$window,
                  estimate, std.error, statistic, p.value,
                  n_obs = nobs(x$models$att))
    })
  })
) %>%
  left_join(outcome_spec %>% select(outcome = col, label), by = "outcome") %>%
  mutate(
    ci_lo = estimate - 1.96 * std.error,
    ci_hi = estimate + 1.96 * std.error,
    sig   = case_when(p.value < .001 ~ "***", p.value < .01 ~ "**",
                      p.value < .05  ~ "*",   TRUE ~ "")
  ) %>%
  arrange(outcome, window, method)

comparison %>%
  mutate(across(c(estimate, std.error, ci_lo, ci_hi), ~ round(.x, 3))) %>%
  select(label, window, method, estimate, std.error, ci_lo, ci_hi, sig, p.value, n_obs) %>%
  print(n = 100)
```

The count below compares how many primary-outcome tests come back significant
against how many would be expected by chance at the 5% level, which is the
multiple-testing question quantified rather than argued.
```{r}
# How many of the primary-outcome tests are significant, and how many would we
# expect by chance? (The multiple-testing defence, quantified.)
prim <- comparison %>% filter(outcome %in% outcome_spec$col[outcome_spec$primary])
tibble(
  n_tests            = nrow(prim),
  n_sig_05           = sum(prim$p.value < .05),
  expected_by_chance = round(0.05 * nrow(prim), 2),
  which_sig          = paste(with(prim[prim$p.value < .05, ],
                             paste0(label, "/", method, "/", window, "d")), collapse = "; ")
)
```

## 6.2 Joint Pre-Trend Tests
These p-values are reported alongside every event study. A low p-value
indicates the counterfactual is a poor fit for that outcome and window.
```{r}
pretrends <- bind_rows(
  map_dfr(did_results, function(r) {
    map_dfr(outcome_cols, function(oc) {
      r$models[[oc]]$pretrend %>%
        mutate(method = "Stacked DiD", outcome = oc, window = r$window)
    })
  }),
  map_dfr(synth_results, function(r) {
    map_dfr(outcome_cols, function(oc) {
      x <- r$by_outcome[[oc]]
      if (is.null(x)) return(NULL)
      x$models$pretrend %>%
        mutate(method = "Synthetic Control DiD", outcome = oc, window = r$window)
    })
  })
) %>%
  left_join(outcome_spec %>% select(outcome = col, label), by = "outcome") %>%
  mutate(chi2 = round(chi2, 2), p_value = round(p_value, 4),
         flag = if_else(p_value < 0.05, "PRE-TREND", "ok")) %>%
  select(label, window, method, chi2, df, p_value, flag) %>%
  arrange(label, window, method)

pretrends %>% print(n = 100)
```

The same results formatted as a display table for the thesis.
```{r}
pretrend_wide <- pretrends %>%
  mutate(
      cell = sprintf("%.3f %s", p_value, if_else(p_value < 0.05, "(fail)", "(pass)"))
  ) %>%
  select(label, window, method, cell) %>%
  pivot_wider(names_from = method, values_from = cell) %>%
  filter(label != "Conditional Discount Depth (%)") %>%   # drop the exploratory outcome
  mutate(label = factor(label, levels = c("Price (USD)", "Sale Frequency",
                                          "Discount Depth (%)"))) %>%
  arrange(label, window) %>%
  rename(Outcome = label, Window = window)

n_fail <- sum(pretrends$p_value < 0.05 &
              pretrends$label != "Conditional Discount Depth (%)", na.rm = TRUE)
n_test <- sum(pretrends$label != "Conditional Discount Depth (%)")

ft_pre <- flextable(pretrend_wide) %>%
  set_header_labels(Window = "Window (days)") %>%
  add_header_row(values = c("", "", "Joint pre-trend test (p-value)"),
                 colwidths = c(1, 1, 2), top = TRUE) %>%
  add_footer_lines(sprintf(
    "H0: all pre-period event-study coefficients = 0 jointly (Wald chi-square, reference week = -1). High p-values support parallel trends. %d of %d tests pass.",
    n_test - n_fail, n_test, 0.05 * n_test)) %>%
  theme_booktabs() %>%
  align(j = 2:4, align = "center", part = "all") %>%
  align(align = "center", part = "header") %>%
  bold(i = ~ Outcome == "Price (USD)" & Window == 90) %>%          # the main finding
  merge_v(j = "Outcome") %>%
  valign(j = "Outcome", valign = "top") %>%
  fontsize(size = 9, part = "footer") %>%
  autofit()

ft_pre

fail_row <- which(pretrend_wide$Outcome == "Price (USD)" & pretrend_wide$Window == 180)
ft_pre <- color(ft_pre, i = fail_row, j = "Synthetic Control DiD", color = "red")

save_as_docx(ft_pre, path = "Output/tab_pretrends.docx")
```

## 6.3 Minimum Detectable Effects
This converts each null into a bounded null. The minimum detectable effect is
the smallest effect the design would detect with 80% power at conventional
significance, reported both in levels and as a share of the pre-period mean.
Read alongside the confidence interval bounds, it establishes which effect
sizes the data rules out rather than merely failing to confirm.
```{r}
pre_means <- steam_panel %>%
  filter(ever_treated, days_since_entry < 0, days_since_entry >= -max(windows)) %>%
  summarise(across(all_of(outcome_cols), ~ mean(.x, na.rm = TRUE))) %>%
  pivot_longer(everything(), names_to = "outcome", values_to = "pre_mean")

mde <- comparison %>%
  left_join(pre_means, by = "outcome") %>%
  mutate(
    mde_80     = 2.8 * std.error,                    # (1.96 + 0.84) * SE
    mde_pct    = round(100 * mde_80 / pre_mean, 1),
    ci_pct_lo  = round(100 * ci_lo / pre_mean, 1),
    ci_pct_hi  = round(100 * ci_hi / pre_mean, 1)
  ) %>%
  select(label, window, method, estimate, pre_mean,
         mde_80, mde_pct, ci_pct_lo, ci_pct_hi) %>%
  mutate(across(c(estimate, pre_mean, mde_80), ~ round(.x, 3)))

mde %>% print(n = 100)
```

## 6.4 Event Studies
```{r fig.width=8, fig.height=5}
dir.create("Output/es", recursive = TRUE, showWarnings = FALSE)

plot_es <- function(mod, ptrend, title, fname) {
  png(file.path("Output/es", fname), width = 8, height = 5, units = "in", res = 220)
  iplot(mod, ref.line = 0, xlab = "Weeks since Epic entry", main = title)
  mtext(sprintf("Joint pre-trend test: chi2(%d) = %.1f, p = %.3f",
                ptrend$df, ptrend$chi2, ptrend$p_value),
        side = 3, line = 0.2, cex = 0.8)
  dev.off()

  iplot(mod, ref.line = 0, xlab = "Weeks since Epic entry", main = title)
  mtext(sprintf("Joint pre-trend test: chi2(%d) = %.1f, p = %.3f",
                ptrend$df, ptrend$chi2, ptrend$p_value),
        side = 3, line = 0.2, cex = 0.8)
}

for (oc in outcome_cols) {
  lab <- outcome_spec$label[outcome_spec$col == oc]
  for (nm in names(did_results)) {
    r <- did_results[[nm]]
    plot_es(r$models[[oc]]$es, r$models[[oc]]$pretrend,
            paste0("Stacked DiD: ", lab, " (", r$window, "d)"),
            paste0("stacked_", oc, "_", r$window, ".png"))
  }
  for (nm in names(synth_results)) {
    r <- synth_results[[nm]]
    x <- r$by_outcome[[oc]]
    if (is.null(x)) next
    plot_es(x$models$es, x$models$pretrend,
            paste0("Synthetic Control DiD: ", lab, " (", r$window, "d)"),
            paste0("synth_", oc, "_", r$window, ".png"))
  }
}
```

## 6.5 Consolidated Results Plot
```{r fig.width=11, fig.height=5}
p_all <- comparison %>%
  filter(outcome %in% outcome_spec$col[outcome_spec$primary]) %>%
  ggplot(aes(x = window, y = estimate, color = method)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray40") +
  geom_pointrange(aes(ymin = ci_lo, ymax = ci_hi),
                  position = position_dodge(width = 8)) +
  geom_line(position = position_dodge(width = 8)) +
  facet_wrap(~ label, scales = "free_y") +
  scale_x_continuous(breaks = windows) +
  labs(title    = "Effect of Epic Listing on Steam Outcomes: Two Estimators",
       subtitle = "Pooled treated x post ATT with 95% CI",
       x = "Window length (days pre/post)", y = "ATT", color = NULL) +
  theme_minimal() + theme(legend.position = "bottom")

p_all
ggsave("Output/es/att_comparison.png", p_all, width = 11, height = 5, dpi = 220)
```

***
# 7. Placebo Tests
## 7.1 In-Time Placebo
Entry is shifted back one full window, so everything inside the fake window is
genuinely pre-treatment and the estimated effect should be zero.
```{r}
placebo_intime <- map_dfr(windows, function(w) {
  n_pre <- floor(w / 7)
  fake_entry <- entry_lookup - w   # shift back one full window

  map_dfr(outcome_spec$col[outcome_spec$primary], function(oc) {
    m <- match_controls(w, n_pre, oc, entry_map = fake_entry)
    if (is.null(m) || nrow(m) == 0) return(NULL)
    d <- build_stacked(m, w, entry_map = fake_entry)
    if (is.null(d) || nrow(d) == 0) return(NULL)
    fit <- feols(as.formula(paste0(oc, " ~ treated:post | subexp^game_title + subexp^event_week")),
                 data = d, cluster = ~ game_title)
    tidy(fit) %>% filter(term == "treated:post") %>%
      transmute(window = w, outcome = oc, estimate, std.error, p.value,
                n_treated = nrow(m))
  })
}) %>%
  left_join(outcome_spec %>% select(outcome = col, label), by = "outcome") %>%
  mutate(across(c(estimate, std.error), ~ round(.x, 3)),
         p.value = round(p.value, 3),
         flag = if_else(p.value < .05, "FAILS PLACEBO", "ok"))

placebo_intime
```

## 7.2 Permutation Placebo
The treated label is randomly reassigned within each matched pair and the model
re-estimated 500 times. Under the null the true estimate should sit in the
middle of this distribution. The resulting p-value makes no distributional
assumptions, so it serves as a check on the cluster-robust p-values reported
above. This is run at the 90-day window, where the one significant price
estimate appears.
```{r}
set.seed(20260630)
N_PERM <- 500

perm_null <- map_dfr(outcome_spec$col[outcome_spec$primary], function(oc) {
  key <- outcome_spec$match_on[outcome_spec$col == oc]
  d   <- did_results$w90$stacked[[key]]
  obs <- coef(did_results$w90$models[[oc]]$att)[["treated:post"]]

  draws <- map_dbl(seq_len(N_PERM), function(i) {
    flip <- tibble(subexp = unique(d$subexp),
                   swap   = sample(c(TRUE, FALSE), n_distinct(d$subexp), replace = TRUE))
    dp <- d %>% left_join(flip, by = "subexp") %>%
      mutate(treated = if_else(swap, 1L - treated, treated))
    coef(feols(as.formula(paste0(oc, " ~ treated:post | subexp^game_title + subexp^event_week")),
               data = dp, cluster = ~ game_title))[["treated:post"]]
  })

  tibble(outcome = oc,
         observed = obs,
         perm_mean = mean(draws),
         perm_sd   = sd(draws),
         pct_more_extreme = mean(abs(draws) >= abs(obs)),
         ri_p = mean(abs(draws) >= abs(obs)))
}) %>%
  left_join(outcome_spec %>% select(outcome = col, label), by = "outcome") %>%
  mutate(across(where(is.numeric), ~ round(.x, 4)))

perm_null
```

***
# 8. Output Tables
Word versions of the result tables for the thesis, plus the diagnostic tables
that went into the appendix and the defense backup slides.
```{r}
library(flextable)
dir.create("Output", showWarnings = FALSE)

att_stacked <- map(setNames(outcome_cols, outcome_cols), function(oc)
  map(did_results, ~ .x$models[[oc]]$att))
att_synth <- map(setNames(outcome_cols, outcome_cols), function(oc)
  map(synth_results, function(r) {
    x <- r$by_outcome[[oc]]; if (is.null(x)) NULL else x$models$att
  }) %>% compact())

make_did_table <- function(oc, oc_label) {
  stk <- att_stacked[[oc]]
  syn <- att_synth[[oc]]

  # Window labels taken from each list separately, in case a synth model failed
  # for some window (then the header still lines up).
  stk_lab <- paste0(sub("^w", "", names(stk)), "d")
  syn_lab <- paste0(sub("^w", "", names(syn)), "d")

  names(stk) <- paste0("S_", stk_lab)
  names(syn) <- paste0("Y_", syn_lab)
  mods <- c(stk, syn)

  ft <- modelsummary(
    mods,
    coef_map = c("treated:post" = "ATT (treated x post)"),
    gof_omit = "R2|AIC|BIC|Log\\.Lik\\.|RMSE|Std\\.Errors|FE:",
    stars    = c('*' = .05, '**' = .01, '***' = .001),
    title    = paste0("Effect of Epic Listing on ", oc_label,
                      ": Stacked vs. Synthetic Control DiD"),
    output   = "flextable"
  )

  mk <- ft$col_keys[-1]
  ft <- set_header_labels(ft,
    values = setNames(as.list(c(stk_lab, syn_lab)), mk))
  ft <- add_header_row(ft,
    values    = c("", "Stacked DiD", "Synthetic Control DiD"),
    colwidths = c(1, length(stk), length(syn)), top = TRUE)

  ft %>% theme_booktabs() %>% align(align = "center", part = "header") %>% autofit()
}

did_price_ft <- make_did_table("price", "Price (USD)")
did_sale_ft  <- make_did_table("sale",  "Sale Frequency")
did_disc_ft  <- make_did_table("disc",  "Discount Depth (%)")
did_cond_ft  <- make_did_table("disc_cond", "Conditional Discount Depth (%)")

did_price_ft; did_sale_ft; did_disc_ft; did_cond_ft

save_as_docx(did_price_ft, did_sale_ft, did_disc_ft, did_cond_ft,
             path = "Output/tab_did_att.docx")

# Diagnostic tables for the appendix / defence backup slides
save_as_docx(
  flextable(stacked_quality) %>% theme_booktabs() %>% autofit(),
  flextable(synth_quality)   %>% theme_booktabs() %>% autofit(),
  flextable(fit_comparison)  %>% theme_booktabs() %>% autofit(),
  flextable(pretrends)       %>% theme_booktabs() %>% autofit(),
  flextable(mde)             %>% theme_booktabs() %>% autofit(),
  flextable(reuse_table)     %>% theme_booktabs() %>% autofit(),
  flextable(balance_table)   %>% theme_booktabs() %>% autofit(),
  flextable(placebo_intime)  %>% theme_booktabs() %>% autofit(),
  flextable(perm_null)       %>% theme_booktabs() %>% autofit(),
  path = "Output/tab_did_diagnostics.docx"
)
```

***
# Extra Information and Code
This section holds code that supported the analysis but does not appear in the
thesis. It is kept because it documents decisions that would otherwise look
arbitrary, particularly the choice of weight solver.

## Verifying How Sale and Discount Depth Are Coded
This determines whether discount depth is a conditional or an unconditional
measure. If discount percent is recorded as 0 on non-sale days rather than as
missing, then the measure is unconditional and is mechanically tied to sale
frequency. That is what this check confirmed, and it is the reason the
conditional measure was added as a fourth outcome.
```{r}
c13 <- data %>%
  filter(shop_name == "Steam") %>%
  summarise(
    n_rows                = n(),
    sale_values           = paste(sort(unique(sale)), collapse = ", "),
    n_disc_NA             = sum(is.na(discount_percent)),
    # what does discount_percent look like when NOT on sale?
    disc_when_not_on_sale_mean   = mean(discount_percent[sale == 0], na.rm = TRUE),
    disc_when_not_on_sale_max    = suppressWarnings(max(discount_percent[sale == 0], 
                                                        na.rm = TRUE)),
    disc_when_not_on_sale_pct_NA = mean(is.na(discount_percent[sale == 0])) * 100,
    # and when on sale?
    disc_when_on_sale_mean       = mean(discount_percent[sale == 1], na.rm = TRUE),
    disc_when_on_sale_median     = median(discount_percent[sale == 1], na.rm = TRUE)
  )
c13
```

## Sparsity of Conditional Discount Depth
Conditional depth is only defined in weeks where a sale actually occurred, and
that condition is itself an outcome. The share of missing game-weeks below is
why it is treated as exploratory rather than as a primary result.
```{r}
tibble(
  pct_weeks_disc_cond_missing_treated = mean(is.na(treated_weekly_cal$disc_cond)) * 100,
  pct_weeks_disc_cond_missing_control = mean(is.na(control_weekly_cal$disc_cond)) * 100
)
```

## Legacy Gradient-Descent Solver
The original synthetic control weights came from a hand-written projected
gradient descent routine with a fixed learning rate and no convergence check.
On price series at typical levels the gradient is large enough that a single
update pushed every weight past zero, after which the clip-and-renormalise step
returned something close to a uniform average of the donors. The function is
kept here only so the comparison below can be reproduced.
```{r}
solve_synth_weights_gd <- function(Y_pre, X_pre, n_iter = 500, lr = 0.01, trace = FALSE) {
  X_pre <- as.matrix(X_pre)
  J <- ncol(X_pre)
  w <- rep(1 / J, J)
  loss <- numeric(n_iter)
  for (it in seq_len(n_iter)) {
    resid    <- as.vector(X_pre %*% w) - Y_pre
    loss[it] <- mean(resid^2)
    grad     <- as.vector(t(X_pre) %*% resid) * (2 / length(Y_pre))
    w        <- w - lr * grad
    w[w < 0] <- 0
    s <- sum(w)
    if (s > 0) w <- w / s else w <- rep(1 / J, J)
  }
  if (trace) attr(w, "loss") <- loss
  w
}
```

## Solver Validation
The symptom that gave the bug away was that the synthetic control was fitting
the pre-period worse than the single nearest-neighbour match. That should be
impossible. A single donor corresponds to a vertex of the feasible simplex, so
a correctly solved synthetic control can always fall back on it and can never
do worse.

The comparison below runs the old solver, the new solver, and the best single
donor on the same donor pool, on levels, so the optimiser is the only thing
that differs. If the old weights are worse than the best single donor, the old
solver is broken. The weight diagnostics show the same thing from the other
direction: a maximum weight close to the minimum weight means the routine never
moved away from its uniform starting point.
```{r}
extract_donor_matrix <- function(tg, w, n_weeks, outcome = "price") {
  E         <- entry_lookup[[tg]]
  entry_cal <- as.integer(floor(as.numeric(E - origin) / 7))
  pre_weeks <- (entry_cal - n_weeks):(entry_cal - 1)
  tr_genres <- treated_info %>% filter(game_title == tg) %>%
    select(all_of(genre_cols)) %>% unlist()

  t_pre <- treated_weekly_cal %>%
    filter(game_title == tg, cal_week %in% pre_weeks) %>%
    transmute(cal_week, y = .data[[outcome]]) %>%
    filter(!is.na(y)) %>% arrange(cal_week)
  if (nrow(t_pre) < 4) return(NULL)

  shared <- as.integer(control_genre_mat %*% tr_genres)
  elig <- control_ranges %>%
    mutate(shared_genres = shared) %>%
    filter(shared_genres >= 1, min_date <= E - w, max_date >= E + w) %>%
    pull(game_title)
  if (length(elig) < 3) return(NULL)

  wide <- control_weekly_cal %>%
    filter(game_title %in% elig, cal_week %in% t_pre$cal_week) %>%
    transmute(game_title, cal_week, value = .data[[outcome]]) %>%
    pivot_wider(names_from = game_title, values_from = value) %>%
    arrange(cal_week)

  X <- wide %>% select(-cal_week)
  keep <- colSums(is.na(X)) == 0
  if (sum(keep) < 3) return(NULL)
  X <- as.matrix(X[, keep, drop = FALSE])
  Y <- t_pre$y[match(wide$cal_week, t_pre$cal_week)]
  ok <- !is.na(Y)
  if (sum(ok) < 4) return(NULL)
  list(Y = Y[ok], X = X[ok, , drop = FALSE], game = tg)
}

rmse <- function(a, b) sqrt(mean((a - b)^2))

set.seed(1)
c1_games <- sample(treated_info$game_title, min(15, nrow(treated_info)))

c1 <- map_dfr(c1_games, function(tg) {
  d <- extract_donor_matrix(tg, 180, floor(180 / 7), "price")
  if (is.null(d)) return(NULL)
  Y <- d$Y; X <- d$X

  w_gd <- solve_synth_weights_gd(Y, X)
  w_qp <- solve_synth_weights(Y, X, demean = FALSE)   # levels: apples-to-apples with GD
  w_tr <- solve_synth_weights(Y, X, demean = TRUE)    # trends: the new default

  best_single <- min(apply(X, 2, function(col) rmse(col, Y)))

  fit_tr  <- as.vector(X %*% w_tr)
  off     <- mean(Y) - mean(fit_tr)

  tibble(
    game            = tg,
    n_donors        = ncol(X),
    n_pre_weeks     = nrow(X),
    rmse_gd_levels  = rmse(as.vector(X %*% w_gd), Y),
    rmse_qp_levels  = rmse(as.vector(X %*% w_qp), Y),
    rmse_best_donor = best_single,
    rmse_qp_trend   = rmse(fit_tr - mean(fit_tr), Y - mean(Y)),   # what DiD actually needs
    rmse_qp_trend_levelrestored = rmse(fit_tr + off, Y),
    # Weight diagnostics
    gd_max_w        = max(w_gd),
    gd_n_eff        = sum(w_gd > 0.01),
    gd_is_uniformish = max(w_gd) - min(w_gd) < 0.02,
    qp_max_w        = max(w_qp),
    qp_n_eff        = sum(w_qp > 0.01)
  )
})

c1 %>% summarise(
  games                = n(),
  mean_rmse_gd_levels  = round(mean(rmse_gd_levels), 2),
  mean_rmse_qp_levels  = round(mean(rmse_qp_levels), 2),
  mean_rmse_best_donor = round(mean(rmse_best_donor), 2),
  mean_rmse_qp_trend   = round(mean(rmse_qp_trend), 2),
  # How often is the old solver worse than the best single donor?
  pct_gd_worse_than_best_single = round(100 * mean(rmse_gd_levels > rmse_best_donor), 1),
  pct_gd_weights_uniform        = round(100 * mean(gd_is_uniformish), 1)
)

c1
```

### Convergence Trace
The loss path for a single treated game, with the best single donor's MSE drawn
as a reference line. A converged solver should end at or below that line.
```{r fig.width=7, fig.height=4}
d <- extract_donor_matrix(c1_games[1], 180, floor(180 / 7), "price")
if (!is.null(d)) {
  w_trace <- solve_synth_weights_gd(d$Y, d$X, trace = TRUE)
  plot(attr(w_trace, "loss"), type = "l",
       xlab = "Iteration", ylab = "MSE",
       main = paste0("Old GD loss path — ", d$game))
  abline(h = min(apply(d$X, 2, function(col) mean((col - d$Y)^2))),
         col = "red", lty = 2)
  legend("topright", legend = c("GD loss", "Best single donor (MSE)"),
         col = c("black", "red"), lty = c(1, 2), bty = "n")
}
```

## Reading the 90-Day Price Result
The one significant price estimate appears at the 90-day window. These three
views pull the relevant rows from tables already shown above, so the estimate,
the fit quality behind it, and its pre-trend test can be read together.
```{r}
comparison %>%
  filter(outcome == "price") %>%
  select(window, method, estimate, std.error, ci_lo, ci_hi, p.value, sig) %>%
  mutate(across(where(is.numeric), ~ round(.x, 3)))

# Fit quality behind each price estimate
fit_comparison %>% filter(matched_on == "price")

# Pre-trend tests behind each price estimate
pretrends %>% filter(label == "Price (USD)")
```
